### 2024-04-02 paper/paper.qmd
Started paper
Added a title, abstract, and introduction

---
title: "Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance"
subtitle: "A reproduction using data from the United States and a case study from Europe" 
author: 
  - Krishiv Jain
thanks: "Code and data are available at: https://github.com/Krishiv-J/ESG-in-Private-Equity"
date: today
date-format: long
abstract: "Concerns have been raised that private equity firms in the United States, who make significant contributions towards both the economy and society, do not give enough importance towards ESG. This paper aims to improve upon the work done and data collected in the ESG in the Top 100 US Private Equity Firms paper by fixing certain data inaccuracies, and considering different variables of interest. The analysis is extended to a case study in Europe. We find that in both regions, the average fund size and their IRR can be used to make reasonable predictions about their focus on ESG, whereas the number of employees that have is irrelevant."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

The corporate landscape is rapidly evolving, with a notable shift towards greater responsibility and transparency, spurred by the rise of Environmental, Social, and Governance (ESG) considerations. While ESG has gained traction in publicly traded companies, there is a significant gap in understanding the ESG practices of private equity (PE) firms, despite their immense global impact. This gap is particularly surprising given the influential role PE firms play in the economy and their potential impact on ESG. This paper aims to address this gap by investigating the determinants and practices of ESG within PE firms.

This paper aims to reproduce the Top 100 US Private Equity Firms paper. That paper focuses on the top 100 PE firms based in the United States, conducting a thorough analysis of their ESG practices through content analysis of their websites. The findings reveal a notable lack of comprehensive ESG disclosures among PE firms, with only a minority providing substantial information on their environmental, social, and governance initiatives. This paper aims to improve upon their work by firstly amending the data collected for certain variables, such as number of employees. Next, this paper calculates next metrics, such as average fund size. Lastly, the paper focuses on different predictor variable. The reasons for each improvement is detailed in the paper.

Understanding the ESG practices of PE firms is crucial for promoting transparency, accountability, and sustainable business practices in the global economy. By uncovering the current state of ESG engagement within PE firms and identifying factors that influence these practices, this study contributes to the broader discourse on corporate responsibility and fills a significant gap in the literature.

This paper is structured as follows. In Section 2, the source of the data, the methodology of data collection and cleaning, and the changes made to the data set is detailed. Section 3 discusses the choice and construction of our logistic model to make predictions about private equity firms. Section 4 presents the model's results. Section 5 draws upon the relevance of these results to Europe. Section 6 talks about the implications, ethical considerations, and limitations of our work.

# Data {#sec-data}

```{r}

```

```{r}

```

# Model

## Model set-up

### Model justification

# Results

```{r}

```

```{r}

```

# Discussion

## First discussion point {#sec-first-point}

## Second discussion point

## Third discussion point

## Weaknesses and next steps

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

```{r}

```

## Diagnostics

```{r}

```

\newpage

# References

### 2024-04-15 scripts/02-data_cleaning.R
Updated Data Cleaning
Removed more columns from the data

@@ -14,7 +14,10 @@ library(arrow)
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 employee_data <- read_csv("data/raw_data/employee_data.csv")
 
-# Remove Unneeded Columns #
+### Remove Unneeded Columns ###
+
+
+## Removing "general" information ##
 
 raw_data$established <- NULL
 raw_data$International <- NULL
@@ -26,12 +29,37 @@ raw_data$WestCoast <- NULL
 raw_data$OtherUSLocation <- NULL
 raw_data$Total_EorSDocsOrMedia <- NULL
 raw_data$Total_EorSDocsOrMedia_2 <- NULL
+raw_data$VCGrowthCapital <- NULL
+raw_data$Firm_age <- NULL
+
+## Removing Calculated Greenwashing Columns ##
+
+raw_data$E_GreenwashingScore_1 <- NULL
 raw_data$Total_GreenwashingScore_1 <- NULL
 raw_data$Total_GreenwashingScore_2 <- NULL
 raw_data$Other_GreenwashingScore_1 <- NULL
 raw_data$Other_GreenwashingScore_2 <- NULL
-raw_data$VCGrowthCapital <- NULL
-raw_data$Firm_age <- NULL
+raw_data$High_Frameworks <- NULL
+raw_data$Medium_Frameworks <- NULL
+raw_data$Low_Frameworks <- NULL
+raw_data$Low_Medium_Frameworks <- NULL
+
+## Removing Information used to calculate High/Low Framework ##
+
+raw_data$Other_AlignwithSDGs <- NULL
+raw_data$Other_AdoptSASBstandards <- NULL
+raw_data$S_SponsorLevel20 <- NULL
+raw_data$E_AdoptTCFD <- NULL
+raw_data$E_CarbonNeutralProtocolCert <- NULL
+raw_data$E_SignatoryNetZeroAsset <- NULL  
+raw_data$E_SignatorytoICI <- NULL
+raw_data$Other_SignatoryPRI <- NULL
+raw_data$Other_AdoptAICGuidelines <- NULL
+raw_data$S_SignatoryILPADiversity <- NULL
+raw_data$S_SignatoryCEOAction <- NULL
+
+
+
 raw_data$Log_Staffcount <- NULL
 raw_data$LogFundSize_Calvin <- NULL
 raw_data$LogFundSize_Preqin <- NULL
[…]

### 2024-04-15 scripts/02-data_cleaning.R
More Data Cleaning

@@ -35,6 +35,9 @@ raw_data$Firm_age <- NULL
 ## Removing Calculated Greenwashing Columns ##
 
 raw_data$E_GreenwashingScore_1 <- NULL
+raw_data$E_GreenwashingScore_2 <- NULL
+raw_data$S_GreenwashingScore_1 <- NULL
+raw_data$S_GreenwashingScore_2 <- NULL
 raw_data$Total_GreenwashingScore_1 <- NULL
 raw_data$Total_GreenwashingScore_2 <- NULL
 raw_data$Other_GreenwashingScore_1 <- NULL
@@ -75,6 +78,17 @@ raw_data$MissingIRR <- NULL
 raw_data$BuyoutFund <- NULL
 raw_data$Sum_wtvpi <- NULL
 raw_data$Totalfundsraised10yearsmn <- NULL
+
+raw_data$E_ALLSignatory <- NULL
+raw_data$S_ALLSignatory <- NULL
+raw_data$E_navigationalpage <- NULL
+raw_data$S_navigationalpage <- NULL
+raw_data$S_DEIpolicy <- NULL
+raw_data$S_DEIcommittee <- NULL
+raw_data$S_ChiefDiversityOfficer <- NULL
+raw_data$S_10pctWomeninBoard <- NULL
+raw_data$S_10pctWomeninLeadership <- NULL
+
 
 ## Removing Weighted Scores ##
 

### 2024-04-15 scripts/02-data_cleaning.R
Data Cleaning

@@ -88,6 +88,12 @@ raw_data$S_DEIcommittee <- NULL
 raw_data$S_ChiefDiversityOfficer <- NULL
 raw_data$S_10pctWomeninBoard <- NULL
 raw_data$S_10pctWomeninLeadership <- NULL
+raw_data$E_HasDocumentsorPages <- NULL
+raw_data$S_HasDocumentsorPages <- NULL
+raw_data$E_HasDocsOrMedia	<- NULL
+raw_data$E_HasDocsOrMedia_2	<- NULL
+raw_data$S_HasDocsOrMedia	<- NULL
+raw_data$S_HasDocsOrMedia_2 <- NULL
 
 
 ## Removing Weighted Scores ##

### 2024-04-16 scripts/02-data_cleaning.R
Data cleaning

@@ -31,6 +31,9 @@ raw_data$Total_EorSDocsOrMedia <- NULL
 raw_data$Total_EorSDocsOrMedia_2 <- NULL
 raw_data$VCGrowthCapital <- NULL
 raw_data$Firm_age <- NULL
+raw_data$Other_ALLFramework <- NULL
+raw_data$G_navigationalpage <- NULL
+raw_data$G_document <- NULL
 
 ## Removing Calculated Greenwashing Columns ##
 
@@ -88,8 +91,8 @@ raw_data$S_DEIcommittee <- NULL
 raw_data$S_ChiefDiversityOfficer <- NULL
 raw_data$S_10pctWomeninBoard <- NULL
 raw_data$S_10pctWomeninLeadership <- NULL
-raw_data$E_HasDocumentsorPages <- NULL
-raw_data$S_HasDocumentsorPages <- NULL
+raw_data$E_document <- NULL
+raw_data$S_document <- NULL
 raw_data$E_HasDocsOrMedia	<- NULL
 raw_data$E_HasDocsOrMedia_2	<- NULL
 raw_data$S_HasDocsOrMedia	<- NULL

### 2024-04-16 scripts/02-data_cleaning.R
Updated Data Cleaning

@@ -34,6 +34,11 @@ raw_data$Firm_age <- NULL
 raw_data$Other_ALLFramework <- NULL
 raw_data$G_navigationalpage <- NULL
 raw_data$G_document <- NULL
+raw_data$Other_ChiefESGofficer <- NULL
+raw_data$Other_ESGcommittee <- NULL
+raw_data$Other_ESGmicrosite <- NULL
+raw_data$Other_ESGsectionvisible <- NULL
+raw_data$Other_SignatoryESGConvergence <- NULL
 
 ## Removing Calculated Greenwashing Columns ##
 
@@ -97,7 +102,6 @@ raw_data$E_HasDocsOrMedia	<- NULL
 raw_data$E_HasDocsOrMedia_2	<- NULL
 raw_data$S_HasDocsOrMedia	<- NULL
 raw_data$S_HasDocsOrMedia_2 <- NULL
-
 
 ## Removing Weighted Scores ##
 

### 2024-04-16 scripts/02-data_cleaning.R
Data Cleaning
Added a calculation for the ESG Score

@@ -14,7 +14,7 @@ library(arrow)
 raw_data <- read_csv("data/raw_data/raw_data.csv")
 employee_data <- read_csv("data/raw_data/employee_data.csv")
 
-### Remove Unneeded Columns ###
+#### Remove Unneeded Columns ####
 
 
 ## Removing "general" information ##
@@ -39,6 +39,21 @@ raw_data$Other_ESGcommittee <- NULL
 raw_data$Other_ESGmicrosite <- NULL
 raw_data$Other_ESGsectionvisible <- NULL
 raw_data$Other_SignatoryESGConvergence <- NULL
+raw_data$Log_Staffcount <- NULL
+raw_data$LogFundSize_Calvin <- NULL
+raw_data$LogFundSize_Preqin <- NULL
+raw_data$Public <- NULL
+raw_data$FundSize_Calvin <- NULL
+raw_data$Sum_wirr_all <- NULL
+raw_data$Diversified <- NULL
+raw_data$Healthcare <- NULL
+raw_data$Technology <- NULL
+raw_data$ConsumerGoods <- NULL
+raw_data$OtherIndustry <- NULL
+raw_data$MissingIRR <- NULL
+raw_data$BuyoutFund <- NULL
+raw_data$Sum_wtvpi <- NULL
+raw_data$Totalfundsraised10yearsmn <- NULL
 
 ## Removing Calculated Greenwashing Columns ##
 
@@ -69,23 +84,7 @@ raw_data$Other_AdoptAICGuidelines <- NULL
 raw_data$S_SignatoryILPADiversity <- NULL
 raw_data$S_SignatoryCEOAction <- NULL
 
-
-
-raw_data$Log_Staffcount <- NULL
-raw_data$LogFundSize_Calvin <- NULL
-raw_data$LogFundSize_Preqin <- NULL
-raw_data$Public <- NULL
-raw_data$FundSize_Calvin <- NULL
-raw_data$Sum_wirr_all <- NULL
-raw_data$Diversified <- NULL
-raw_data$Healthcare <- NULL
-raw_data$Technology <- NULL
-raw_data$ConsumerGoods <- NULL
-raw_data$OtherIndustry <- NULL
-raw_data$MissingIRR <- NULL
-raw_data$BuyoutFund <- NULL
-raw_data$Sum_wtvpi <- NULL
-raw_data$Totalfundsraised10yearsmn <- NULL
[…]

### 2024-04-16 scripts/02-data_cleaning.R
Finished Data Cleaning
Finished the data cleaning script

@@ -145,7 +145,26 @@ raw_data$ESG_Score <- (raw_data$HasESGonWebsite + raw_data$E_Portfoliocasestudie
                          raw_data$S_HasDocumentsorPages + raw_data$G_HasDocumentsorPages +
                          raw_data$Other_HasESGHeadorCommittee)
 
-
+#### Remove Columns used in Calculation ####
+raw_data$HasESGonWebsite <- NULL
+raw_data$E_Portfoliocasestudies <- NULL
+raw_data$E_Media <- NULL
+raw_data$S_Portfoliocasestudies <- NULL
+raw_data$S_Media <- NULL
+raw_data$G_Portfoliocasestudies <- NULL
+raw_data$Other_ESGfund <- NULL
+raw_data$Other_ESGdocument <- NULL
+raw_data$Other_Portfoliocasestudies <- NULL
+raw_data$Other_ESGMedia <- NULL
+raw_data$Other_ESGpolicy <- NULL
+raw_data$Other_ESGreport <- NULL
+raw_data$Other_ESGAwards  <- NULL
+raw_data$E_HasDocumentsorPages <- NULL
+raw_data$S_HasDEI <- NULL
+raw_data$S_10PctWomenBoardExec <- NULL
+raw_data$S_HasDocumentsorPages <- NULL
+raw_data$G_HasDocumentsorPages <- NULL
+raw_data$Other_HasESGHeadorCommittee <- NULL
 
 #### Save data ####
 write_csv(raw_data, "data/analysis_data/cleaned_data1.csv")

### 2024-04-17 scripts/02-data_cleaning.R
Saving my work

@@ -127,7 +127,7 @@ raw_data$Total_WeightedESGScore_8 <- NULL
 
 #### Add Column for New Employee ####
 raw_data$Staffcounttotal <- NULL
-raw_data$Staff <- employee_data$`No. of Employees`
+raw_data$Staff_Count <- employee_data$`No. of Employees`
 
 #### Add Column for Average Fund Size ####
 raw_data$Average_Fund_Size <- (raw_data$FundSize_Preqin/raw_data$Totalnumberoffunds)

### 2024-04-17 scripts/04-model.R

@@ -11,9 +11,19 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(modelsummary)
+library(dplyr)
+
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
+
+
+
+analysis_data1 <- analysis_data %>% 
+  filter(ESG_Score != 0)
+
+
 
 ### Model data ####
 first_model <-
@@ -27,6 +37,35 @@ first_model <-
     seed = 853
   )
 
+esg_neg_binomial <- stan_glm(
+  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
+  data = analysis_data1,
+  family = neg_binomial_2(link = "log"),
+  seed = 555
+)
+
+
+esg_neg_binomial5 <- stan_glm(
+  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
+  data = analysis_data1,
+  family = neg_binomial_2(link = "identity"),
+  seed = 555
+)
+
+
+esg_neg_binomial1 <- stan_glm(
+  ESG_Score ~ Totalnumberoffunds,
+  data = analysis_data1,
+  family = neg_binomial_2(link = "identity"),
+  seed = 555
+)
+
+esg_neg_binomial2 <- stan_glm(
+  ESG_Score ~  Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
+  data = analysis_data1,
+  family = neg_binomial_2(link = "log"),
+  seed = 555
+)
 
 #### Save model ####
 saveRDS(

### 2024-04-18 paper/paper.qmd
Data Section
Added the data section to the paper.

@@
 library(palmerpenguins)
+library(here) 
+library(knitr)
+library(janitor)
+library(arrow)
 ```
@@
 
+## Source and Collection
+
+The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper (CITE), which was published in July 2023. The data was collected for the year 2022.
+
+The authors selected the top 100 U.S.-based private equity firms for the year 2022.
+This selection was guided by the rankings from Private Equity International, a renowned organisation that publishes an annual global ranking of PE firms.
+The rankings are based on fundraising amounts in millions of dollars over the preceding five years, providing a reliable measure of each firm's market presence and activity.
+The choice of U.S.
+firms was deliberate, as they wield significant global influence and impact.
+Furthermore, limiting the study to U.S.
+firms helped eliminate potential variations that may arise from country-specific factors, given that the top non-U.S.
+firms were spread across various countries with diverse regulatory environments.
+Whilst this subset represents only a fraction of the total number of private equity firms, it accounted for over 25% of the total committed capital and employed more than 26% of the industry's workforce in 2022.
+
+To ensure the sample captured firms primarily dedicated to private equity, the authors excluded investment banks like Goldman Sachs or Blackrock, despite their presence in the Private Equity International rankings.
+These institutions were excluded due to their diversified operational structure, which includes private equity as a tertiary segment rather than a primary focus.
+
+The selection criteria also took into account the primary investment strategies of the firms.
+While private equity firms typically engage in strategies such as buyouts, growth equity, and venture capital, some may have alternative approaches like management buy-ins, impact investing, or infrastructure investing.
+To maintain consistency and focus, the authors excluded firms that did not prioritise private equity as their primary investment strategy.
+
+In cases where a firm was excluded or did not meet the predetermined criteria, the authors substituted it with the subsequent firm from the 2022 Private Equity International rankings.
+This approach ensured that the sample size reached the intended count of 100 while maintaining the integrity of the data.
+As such, the sample stops at the private equity firm
+ranking 116.
+
+For the data collection process, the authors hand-collected the data to ensure its accuracy.
+The authors primarily relied on content analysis of the firms' websites.
+This method has a long-standing history in analysing company-related information.
+The websites provided a rich source of information, including financial reports, dedicated ESG microsites, documents, informational videos, interviews, and management letters.
+This extensive review aimed to capture all firm-level ESG-related information.
+
+To ensure the data's reliability and validity, the authors adopted a coding system that aimed to distinguish between genuine involvement in ESG practices and mere lip service.
+While documents and presentations with substantial ESG-related content were included, boilerplate language lacking supporting material was excluded.
+
+The majority of data on the specific characteristics of the private equity firms, such as size, staff count, investment strategy, total number of funds, and more, were extracted from Preqin.
+
+## Modifications made
+
+### Variables
+
+The original dataset had 117 columns (1 column for the name of the firm, and 116 for various data points for each of the 100 firms).
+In analysing the determinants of ESG activities, the authors considered a range of PE firm-level variables.
+The authors organised the ESG information from the firms' websites into distinct content categories to capture various aspects of their practices.
+Initially, the results were classified into four main groups: Environmental (E), Social (S), Governance (G), and an "Other" category, which encompasses ESG aspects that do not fit neatly into the environmental, social, or governance classifications.
+Each of these primary categories was further divided into two sub-categories.
+The first sub-category contributes to the respective E, S, G, or "Other" score, while the second focuses on ESG frameworks, signatories, certifications, or sponsorships.
+The authors also created a “weighted” ESG-Score.
+Finally, the authors also assessed the private equity firms' explicit commitments to ESG frameworks beyond the ESG score.
+This involved evaluating whether the firms align with specific ESG frameworks, participate in related initiatives, hold ESG certifications, and engage in ESG sponsorships.
+In doing so, the paper aimed to determine if the firm was engaging in greenwashing, which is the deceptive practice of exaggerating or falsely claiming environmentally friendly initiatives [@green].
+Given the focus of this paper, any variable used for the analysis of the firm's greenwashing was excluded.
+
+#### Staff Count
+
+It was observed that the count for the number of employees was significantly inaccurate.
+For instance, Sequoia Capital was reported having only 19 employees.
+Thus, to fix the dataset, data from the LinkedIn pages of each firm was used.
+For each company on LinkedIn, there is a section that includes the number of people that are currently employed by the firm.
+LinkedIn reported Sequoia as having 824 employees, a significant difference from the 19 employees previously reported.
+The implication of using this methodology is discussed further below.
+Energy & Minerals Group’s LinkedIn’s page could not be found, thus, the original number reported was used.
+
+#### Internal Rate of Return
+
+The Internal Rate of Return (IRR) was gathered from the Preqin.
+Whilst Preqin provided comprehensive data for most of the utilised variables, there were some gaps that were filled in manually.
+Specifically, there were 22 missing observations for IRR.
+
+To address these gaps, the authors sourced the missing data from Bloomberg, bringing the total IRR observations to 96 out of the 100 firms in the sample.
+However, once again, it was observed that the data obtained from Bloomberg was significantly inaccurate.
+For instance, PSG’s IRR was taken from Bloomberg since Preqin did not have data.
+It was reported to be 78.8%.
+However, a presentation from PSG reported their 2022 gross IRR as 56%, and their net IRR as 44% [@PSG].
+Thus, despite the lower number of observations, Preqin’s data was used given its higher accuracy.
+
+#### Variables removed from regression
+
+Moreover, a number of variables that were used in the original paper as predictor variables in their regression were removed:
+
+- `Public`: A dummy variable indicating whether the private equity firm is publicly traded.
+- `IRR (All)`: The overall Internal Rate of Return (IRR) of the private equity firm, from either of Preqin and Bloomberg
+- `Buyout`: A dummy variable indicating whether the private equity firm specialises in buyout investments.
+- `VC or Growth Capital`: A dummy variable indicating whether the private equity firm is a Venture Capital firm or specialised in Growth Capital.
+- `Avg.Vintage`: The average vintage year of the funds within the private equity firm.
+- `EastCoast`: A dummy variable indicating whether the private equity firm is located on the East Coast.
+- `WestCoast`: A dummy variable indicating whether the private equity firm is located on the West Coast.
+- `OtherUSLocation`: A dummy variable indicating whether the private equity firm is in another US Location, other than the East Coast or West Coast.
+- `Total Number of Funds`: The total number of funds within the private equity firm.
+
+### Methodology
+
+The authors' methodology for calculating the ESG-Score involves aggregating scores from four distinct categories: Environmental (E-Score), Social (S-Score), Governance (G-Score), and Other-Score.
+For each score, various data points collected for related to each specific subcategory, such as environmental initiatives for the E-Score, social considerations for the S-Score, and governance practices for the G-Score, are averaged.
+The Other-Score captures miscellaneous ESG-related factors like award recognition and dedicated ESG funds.
+For each category, a score of 1 indicates optimal performance in that aspect of ESG, while a score of 0 suggests a lack of effort or data.
+The scores are then added to produce an overall ESG-Score that ranges from 0 to 4.
+A score of 0 signifies a complete absence of ESG practices, whereas a score of 4 represents exemplary ESG commitment.
+
+In this paper, the approach to calculating the ESG-Score diverges from the original methodology by opting for a summing method rather than averaging across the categories.
+This decision was driven by the desire to give equal weight to each component, ensuring that a firm's commitment across different ESG aspects is considered equally important.
+By summing the scores, the methodology emphasises the cumulative presence and effort towards ESG across all categories.
+This approach rectifies the potential imbalance that could arise when averaging, where fewer factors in one category could have the same weight as a larger number in another, leading to a more balanced and comprehensive assessment of a firm's ESG practices.
+In total, 23 columns are added to calculate the ESG Score.
+A value of 0 indicates that the firm does not engage in any form of ESG, whilst a score of 23 indicates optimal ESG practices.
+APPENDIX is a list of every variable included in the calculation of the ESG Score.
+
+Furthermore, in their methodology, the authors adopted a weighted approach for calculating the ESG score, termed the Weighted ESG-Score.
+This method aggregates the scores of each E, S, G, and “Other” factors, with the E-Score and Other-Score, both heavy in environmental factors, given twice the weight of the S-Score and G-Score.
+Their rationale for this weighting is rooted in the heightened interest in environmental issues compared to other aspects of ESG.
+However, in this study, the Weighted ESG-Score was omitted for several reasons.
+First, there's the potential for bias in weighting; assigning environmental factors double the weight could skew the scoring system.
+Without a universally agreed-upon weighting scheme, scores may become subjective, compromising interpretability and comparability.
+Second, by excluding the weighted approach, the study adopts a more holistic perspective on ESG, treating each factor equally.
+This ensures that no single ESG component is prioritised over the others.
+
+## Data Cleaning
+
+After converting the dataset from its original Stata file type to csv, a column for the Average Fund Size variable was added.
+This was calculated as the Fund Size divided by the Number of Funds.
+This was done as larger fund sizes might indicate more resources available for ESG initiatives, potentially correlating with a stronger ESG commitment.
+The data for the number of employees was also added to the table.
+All the unneeded columns, including the ones mentioned before, and other unneeded ones, such as the year the PE firm was established were removed.
+Furthermore, there were repetitive columns, columns with no description throughout the paper, and any columns that were used to calculate other columns that were removed.
+For instance, three individual columns indicating the presence of a DEI policy, a Chief Diversity Officer, and a DEI committee were removed during the data cleaning process.
+These columns became redundant as their information was already consolidated into a single DEI column.
+The DEI column effectively captures the combined presence of these components, making the individual columns unnecessary.
+
+Next, the ESG score was calculated using the methodology detailed above.
+After doing so, all the columns used in its calculation were also deleted since they were not needed anymore, leaving the final data set looking like FIGURE 10.
+
 ```{r}
+#| label: fig-1
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: "Total Number of Funds vs ESG Score"
+#| fig-pos: H
+
+analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
+
+ggplot(analysis_data, aes(x = Totalnumberoffunds, y = ESG_Score)) +
+  geom_point() +
+  labs(x = "Total Number of Funds", 
+       y = "ESG Score", 
+       title = "Total Number of Funds vs ESG Score")
 

### 2024-04-18 scripts/02-data_cleaning.R

@@ -132,7 +132,7 @@ raw_data$Staff_Count <- employee_data$`No. of Employees`
 #### Add Column for Average Fund Size ####
 raw_data$Average_Fund_Size <- (raw_data$FundSize_Preqin/raw_data$Totalnumberoffunds)
 
-#### Add Column for ESG Score ####
+#### Calculate and Add Column for ESG Score ####
 
 raw_data$ESG_Score <- (raw_data$HasESGonWebsite + raw_data$E_Portfoliocasestudies +
                          raw_data$E_Media + raw_data$S_Portfoliocasestudies +

### 2024-04-18 paper/paper.qmd
Completed Data Section

@@
 library(arrow)
+library(here)
+library(gridExtra)
+
+analysis_data <- read_csv(here("data/analysis_data/cleaned_data1.csv"))
 ```
@@
 Next, the ESG score was calculated using the methodology detailed above.
-After doing so, all the columns used in its calculation were also deleted since they were not needed anymore, leaving the final data set looking like FIGURE 10.
+After doing so, all the columns used in its calculation were also deleted since they were not needed anymore.
+A snippet of the first 10 firms is seen in @tbl-1.
+Moreover, @fig-2, @fig-4, @fig-3 demonstrate the correlations between each firm characteristics, and their ESG Score.
 
 ```{r}
-#| label: fig-1
+#| label: tbl-1
 #| echo: false
@@
 #| message: false
-#| fig-cap: "Total Number of Funds vs ESG Score"
-#| fig-pos: H
+#| tbl-cap: "First 10 Private Equity Firms in the cleaned dataset"
+#| tbl-pos: H
 
-analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
-
-ggplot(analysis_data, aes(x = Totalnumberoffunds, y = ESG_Score)) +
-  geom_point() +
-  labs(x = "Total Number of Funds", 
-       y = "ESG Score", 
-       title = "Total Number of Funds vs ESG Score")
+analysis_data |>
+  mutate(
+    Sum_wirr_preqin = round(Sum_wirr_preqin, 2),
+    Average_Fund_Size = round(Average_Fund_Size, 2)
+  ) |>
+  head(10) |>
+  kable(
+    col.names = c("Firm", "No. of Funds", "Fund Size", "IRR", "Staff", "Average Fund Size", "ESG Score")
+  )
 
@@
 ```{r}
+#| label: fig-2
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: "ESG Score by IRR and Staff Count"
+#| fig-pos: H
+
+irr <- ggplot(analysis_data, aes(x = Sum_wirr_preqin, y = ESG_Score)) +
+  geom_point() +
+  labs(title = "Internal Rate of Return vs ESG Score",
+       x = "Internal Rate of Return",
+       y = "ESG Score") +
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5))
+
+staff <- ggplot(analysis_data, aes(x = Staff_Count, y = ESG_Score)) +
+  geom_point() +
+  labs(title = "Number of Employees vs ESG Score",
+       x = "Number of Employees",
+       y = "ESG Score") +
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5))
+
+grid.arrange(staff, irr, 
+               ncol = 2
+)
+```
+
+```{r}
+#| label: fig-4
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: "ESG Score by IRR and Staff Count"
+#| fig-pos: H
+
+number_of_funds <- ggplot(analysis_data, aes(x = Totalnumberoffunds, y = ESG_Score)) +
+  geom_point() +
+  labs(title = "Total Number of Funds vs ESG Score",
+       x = "Total Number of Funds",
+       y = "ESG Score") +
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5))
+
+size <- ggplot(analysis_data, aes(x = FundSize_Preqin, y = ESG_Score)) +
+  geom_point() +
+  labs(title = "Fund Size vs ESG Score",
+       x = "Fund Size",
+       y = "ESG Score") +
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5))
+
+grid.arrange(number_of_funds, size, 
+               ncol = 2
+)
+```
+
+```{r}
+#| label: fig-3
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: "ESG Score by Average Fund Size"
+#| fig-pos: H
+
+ggplot(analysis_data, aes(x = Average_Fund_Size, y = ESG_Score)) +
+  geom_point() +
+  labs(title = "Average Fund Size vs ESG Score",
+       x = "Average Fund Size",
+       y = "ESG Score") +
+  theme_minimal() + 
+  theme(plot.title = element_text(hjust = 0.5, size = 10),
+                axis.title.x = element_text(size = 9),
+                axis.title.y = element_text(size = 9),
+        axis.text.y = element_text(size = 7.5)) 
+    plot.margin = unit(c(0.1, 0.1, 0.1, 0.1), "cm")
 

### 2024-04-18 paper/paper.qmd
Added Model Section

@@
 library(gridExtra)
+library(modelsummary)
 
@@
 
-### Model justification
+\begin{align} 
+ESG_i|\pi_i &\sim \mbox{Negative Binomial}(r, \pi_i) \\
+logit(\pi_i) &= \beta_0 + \beta_1 \text{funds}_i + \beta_2  \text{fund\_size}_i + \beta_3 \text{IRR}_i +\beta_4 \text{staff}_i+\beta_5 \text{average\_fund\_size}_i \\
+\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_4 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_5 &\sim \mbox{Normal}(0, 2.5)
+\end{align}
+
+## Model justification
+
+Negative binomial regression offers a robust approach to analyzing count data, especially when the assumption of equal mean and variance, inherent to Poisson regression, is violated.
+This regression model accommodates overdispersion, a common characteristic in count data where the variance exceeds the mean, providing a more flexible framework than the Poisson model.
+In this paper, the negative binomial regression is employed to examine the relationship between firm characteristics and their ESG scores.
+Given the potential for overdispersion in these counts, the negative binomial regression provides a suitable and robust approach to our analysis.
 
@@
 ```{r}
+#| label: tbl-3
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Results"
+#| tbl-pos: H
+
+#### Read data ####
+analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
+
+### Model data ####
+
+esg_model <- stan_glm(
+  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
+  data = analysis_data,
+  family = neg_binomial_2(link = "identity"),
+  seed = 555
+)
+
+modelsummary(esg_model)
 

### 2024-04-18 scripts/04-model.R

@@ -13,64 +13,27 @@ library(tidyverse)
 library(rstanarm)
 library(modelsummary)
 library(dplyr)
+library(tidyr)
 
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
 
-
-
-analysis_data1 <- analysis_data %>% 
-  filter(ESG_Score != 0)
-
-
-
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
 
-esg_neg_binomial <- stan_glm(
+esg_model <- stan_glm(
   ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
-  data = analysis_data1,
-  family = neg_binomial_2(link = "log"),
-  seed = 555
-)
-
-
-esg_neg_binomial5 <- stan_glm(
-  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
-  data = analysis_data1,
+  data = analysis_data,
   family = neg_binomial_2(link = "identity"),
   seed = 555
 )
 
-
-esg_neg_binomial1 <- stan_glm(
-  ESG_Score ~ Totalnumberoffunds,
-  data = analysis_data1,
-  family = neg_binomial_2(link = "identity"),
-  seed = 555
-)
-
-esg_neg_binomial2 <- stan_glm(
-  ESG_Score ~  Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
-  data = analysis_data1,
-  family = neg_binomial_2(link = "log"),
-  seed = 555
-)
+modelsummary(esg_model)
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  esg_model,
+  file = "models/esg_model.rds"
 )
 
 

### 2024-04-18 paper/paper.qmd
Model

@@
 library(gridExtra)
-library(modelsummary)
+library(gtsummary)
 
@@
 
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
+esg_model <- readRDS(file = here::here("models/esg_model.rds"))
 
-### Model data ####
-
-esg_model <- stan_glm(
-  ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
-  data = analysis_data,
-  family = neg_binomial_2(link = "identity"),
-  seed = 555
-)
-
-modelsummary(esg_model)
+tbl_regression(esg_model)
 

### 2024-04-18 scripts/04-model.R

@@ -14,6 +14,8 @@ library(rstanarm)
 library(modelsummary)
 library(dplyr)
 library(tidyr)
+library(gtsummary)
+
 
 
 #### Read data ####
@@ -21,14 +23,17 @@ analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
 
 ### Model data ####
 
-esg_model <- stan_glm(
+model <- stan_glm(
   ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
   data = analysis_data,
   family = neg_binomial_2(link = "identity"),
   seed = 555
 )
 
-modelsummary(esg_model)
+modelsummary(model)
+
+tbl_regression(esg_model)
+
 
 #### Save model ####
 saveRDS(

### 2024-04-18 paper/paper.qmd
Trying to fix model

@@
 library(gtsummary)
+library(modelsummary)
 
@@
 
+modelsummary(esg_model)
+
 ```

### 2024-04-18 scripts/04-model.R

@@ -8,21 +8,16 @@
 # Any other information needed? [...UPDATE THIS...]
 
 
-#### Workspace setup ####
+# Load required libraries
 library(tidyverse)
 library(rstanarm)
-library(modelsummary)
-library(dplyr)
-library(tidyr)
+library(broom.mixed)
 library(gtsummary)
-
-
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
 
 ### Model data ####
-
 model <- stan_glm(
   ESG_Score ~ Totalnumberoffunds + FundSize_Preqin + Sum_wirr_preqin + Staff_Count + Average_Fund_Size,
   data = analysis_data,
@@ -30,9 +25,20 @@ model <- stan_glm(
   seed = 555
 )
 
-modelsummary(model)
+# Extract coefficients using broom::tidy
+tidy_model <- broom.mixed::tidy(model)
 
-tbl_regression(esg_model)
+# Create summary table using gtsummary
+summary_table <- tidy_model %>%
+  select(term, estimate, std.error) %>%
+  tbl_summary(
+    by = NULL,
+    statistic = list(estimate ~ "{mean} ({sd})"),
+    digits = list(all_continuous() ~ 2)
+  )
+
+# Print summary table
+summary_table
 
 
 #### Save model ####

### 2024-04-18 scripts/04-model.R
Model Script

@@ -12,7 +12,6 @@
 library(tidyverse)
 library(rstanarm)
 library(broom.mixed)
-library(gtsummary)
 
 #### Read data ####
 analysis_data <- read_csv("data/analysis_data/cleaned_data1.csv")
@@ -24,6 +23,8 @@ model <- stan_glm(
   family = neg_binomial_2(link = "identity"),
   seed = 555
 )
+
+modelsummary(model)
 
 # Extract coefficients using broom::tidy
 tidy_model <- broom.mixed::tidy(model)

### 2024-04-18 paper/paper.qmd
Added more libraries

@@
 
-library(tidyverse)
 library(palmerpenguins)
 library(here) 
-library(knitr)
-library(janitor)
 library(arrow)
@@
 library(gtsummary)
+
+library(boot)
+library(broom.mixed)
+library(collapse)
+library(dataverse)
+library(gutenbergr)
+library(janitor)
+library(knitr)
+library(marginaleffects)
 library(modelsummary)
+library(rstanarm)
+library(tidybayes)
+library(tidyverse)
 

### 2024-04-18 paper/paper.qmd
Model Summary Table

@@
 library(arrow)
-library(here)
 library(gridExtra)
@@
 
-tbl_regression(esg_model)
+tidy_model <- broom.mixed::tidy(esg_model)
 
-```
+tidy_model <- tidy_model %>%
+  mutate(term = case_when(
+    term == "(Intercept)"        ~ "Intercept",
+    term == "Totalnumberoffunds" ~ "Total Number of Funds",
+    term == "FundSize_Preqin"    ~ "Fund Size",
+    term == "Sum_wirr_preqin"    ~ "IRR",
+    term == "Staff_Count"        ~ "Staff",
+    term == "Average_Fund_Size"  ~ "Average Fund Size",
+    TRUE                         ~ term
+  ))
 
-```{r}
-
-modelsummary(esg_model)
+kable(tidy_model, format = "markdown", 
+      col.names = c("Term", "Estimate", "Std. Error"),
+      digits = 3)
 

### 2024-04-18 paper/paper.qmd
Results Section
Added the results section to the paper

@@
 ESG_i|\pi_i &\sim \mbox{Negative Binomial}(r, \pi_i) \\
-logit(\pi_i) &= \beta_0 + \beta_1 \text{funds}_i + \beta_2  \text{fund\_size}_i + \beta_3 \text{IRR}_i +\beta_4 \text{staff}_i+\beta_5 \text{average\_fund\_size}_i \\
+(\pi_i) &= \beta_0 + \beta_1 \text{funds}_i + \beta_2  \text{fund\_size}_i + \beta_3 \text{IRR}_i +\beta_4 \text{staff}_i+\beta_5 \text{avg\_fund\_size}_i \\
 \beta_0 &\sim \mbox{Normal}(0, 2.5) \\
@@
 #| message: false
-#| tbl-cap: "Results"
+#| tbl-cap: "Model Summary of the firm's ESG Score by various firm characteristics"
 #| tbl-pos: H
@@
 ```
+
+@tbl-3 presents the results of the negative binomial regression model examining the relationship between various firm characteristics and their ESG scores.
+The intercept of 0.692 serves as the baseline ESG score when all predictor variables are set to zero, though its practical interpretation is limited.
+
+The coefficient for 'Total Number of Funds' is estimated at 0.0119 with a standard error of 0.0385.
+This suggests that for each additional fund a firm manages, there is an expected increase of 0.0119 in its ESG score, holding other variables constant.
+With a relatively high standard error compared to the coefficient, this suggests that the relationship between the number of funds and ESG score is uncertain.
+The low coefficient value indicates that for each additional fund, the expected increase in ESG score is quite small, and given the standard error, this effect may not be statistically significant.
+
+'Fund Size' has an estimated coefficient of 0.0000350 with a standard error of 0.0000427.
+This relatively low coefficient suggests a negligible impact of fund size on ESG scores.
+The standard error is also relatively high, indicating uncertainty around this estimate.
+
+'IRR' has an estimated coefficient of 0.116 with a standard error of 0.0830.
+This suggests that a 1 unit increase in IRR is associated with an expected increase of 0.116 in the ESG score.
+Whilst the coefficient suggests a positive relationship between IRR and ESG scores, the high standard error indicates a considerable amount of uncertainty around this estimate.
+Given the magnitude of the standard error, the relationship between IRR and ESG scores may not be robust.
+
+For 'Staff', the estimated coefficient is 0.000914 with a standard error of 0.00109.
+The low coefficient suggests a minimal impact of staff count on ESG scores.
+Additionally, the standard error is relatively high compared to the coefficient, implying uncertainty in this relationship.
+
+Lastly, 'Average Fund Size' has an estimated coefficient of 0.0000386 with a standard error of 0.000529.
+Similar to the 'Fund Size', the low coefficient and high standard error suggest that the impact of average fund size on ESG scores is negligible and uncertain.
+
+In summary, whilst some variables like 'Total Number of Funds' and 'IRR' show positive associations with ESG scores, the low coefficient values coupled with high standard errors suggest these relationships are weak and potentially not statistically significant.
+On the other hand, 'Fund Size', 'Staff', and 'Average Fund Size' exhibit negligible.
+effects on the firm's ESG score.
 

### 2024-04-18 paper/paper.qmd
Stimulate and Test Data
Updated the scripts to stimulate and test the datasets

@@
 Section 6 talks about the implications, ethical considerations, and limitations of our work.
+
+The estimand for this paper is the effect of various firm-specific factors (Total Number of Funds, Fund Size, IRR, Staff Count, and Average Fund Size) on a private equity firm's ESG scores.
 
@@
 
-## First discussion point {#sec-first-point}
+## Findings and Comparison
 
-## Second discussion point
+The results from the negative binomial regression model provide insights into the factors influencing ESG scores in private equity firms.
+The findings suggest that 'Total Number of Funds' and 'IRR' are positively associated with ESG scores, although with relatively modest coefficients and high standard errors.
+Conversely, 'Fund Size', 'Staff', and 'Average Fund Size' demonstrate negligible impact on ESG scores.
 
-## Third discussion point
+Comparing these results to PAPER, there are several similarities and differences.
+In the original paper, neither 'IRR (Preqin)' nor 'IRR (All)' showed significant influence on ESG scores.
+In contrast, this paper's results identify a positive relationship between IRR and ESG scores.
+This discrepancy suggests that firm performance, as measured by IRR, might indeed predict ESG activities.
+The original paper also considered the variables 'Log Fund Size' and 'Staff Count' as potential regressors, and found that neither variable had a statistically significant relation with a firm's ESG Score.
+This paper did not apply a log to the fund size, and had replaced the data for staff (instead of using Preqin's data, LinkedIn's data was used).
+However, despite the aforementioned changes to the data,this paper also found that neither of these two variables had a significant relation with ESG scores.
 
-## Weaknesses and next steps
+## Weaknesses
+
+## Future Research
 

### 2024-04-18 scripts/00-simulate_data.R

@@ -1,19 +1,47 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulates the data sets 
+# Author: Krishiv Jain
+# Date: 18 April 2024
+# Contact: krishiv.jain@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: none
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
-#### Simulate data ####
-# [...ADD CODE HERE...]
+#### SIMULATE DATA ####
 
+set.seed(555) #random seed
 
+# Stimulating the dataset
 
+simulated_data <-  
+  tibble(
+    Firm = rep(1:100),    
+    Funds = round(runif(100, min = 0, max = 200)),
+    Fund_Size = runif(100, min = 100, max = 50000),
+    IRR = runif(100, min = 0, max = 100),
+    Staff_Count = round(runif(100, min = 0, max = 10000)),
+    Average_Fund_Size = Fund_Size/Funds, 
+    ESG_Score = round(runif(100, min = 0, max = 20)))
+
+#### TEST DATA ####
+
+##Check the minimum number is equal, or greater than, 0 ##
+#Based on: https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html#simulate
+simulated_data$Funds |> min() >= 0
+simulated_data$Staff_Count |> min() >= 0
+
+##Check the class of the column is numeric##
+simulated_data$Funds |> class() == "numeric"
+simulated_data$Fund_Size |> class() == "numeric"
+simulated_data$IRR |> class() == "numeric"
+simulated_data$Staff_Count |> class() == "numeric"
+simulated_data$Average_Fund_Size |> class() == "numeric"
+simulated_data$ESG_Score |> class() == "numeric"
+
+## Check that the columns only have whole numbers ##
+#Based on: https://stackoverflow.com/q/3476782/23271634
+is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) < tol
+is.wholenumber(simulated_data$ESG_Score)
+is.wholenumber(simulated_data$Staff_Count)

### 2024-04-18 scripts/03-test_data.R

@@ -1,15 +1,36 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Testing the data set
+# Author: Krishiv Jain
+# Date: 18 April 2024
+# Contact: krishiv.jain@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Downloaded the cleaned data file from the cleaned_data folder to run these tests
 
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(here)
 
-#### Test data ####
+#### READ DATA ####
+cleaned_data <- read_csv(here("data/analysis_data/cleaned_data1.csv"))
+
+#### TEST DATA ####
+
+##Check the minimum number is equal, or greater than, 0 ##
+#Based on: https://tellingstorieswithdata.com/02-drinking_from_a_fire_hose.html#simulate
+cleaned_data$Totalnumberoffunds |> min() >= 0
+cleaned_data$Staff_Count |> min() >= 0
+
+##Check the class of the column is numeric##
+cleaned_data$Totalnumberoffunds |> class() == "numeric"
+cleaned_data$FundSize_Preqin |> class() == "numeric"
+cleaned_data$Sum_wirr_preqin |> class() == "numeric"
+cleaned_data$Staff_Count |> class() == "numeric"
+cleaned_data$Average_Fund_Size |> class() == "numeric"
+cleaned_data$ESG_Score |> class() == "numeric"
+
+## Check that the columns only have whole numbers ##
+#Based on: https://stackoverflow.com/q/3476782/23271634
+is.wholenumber <- function(x, tol = .Machine$double.eps^0.5) abs(x - round(x)) < tol
+is.wholenumber(cleaned_data$Staff_Count)
+is.wholenumber(cleaned_data$ESG_Score)

### 2024-04-18 scripts/04-model.R
Finalised Scripts

@@ -24,24 +24,6 @@ model <- stan_glm(
   seed = 555
 )
 
-modelsummary(model)
-
-# Extract coefficients using broom::tidy
-tidy_model <- broom.mixed::tidy(model)
-
-# Create summary table using gtsummary
-summary_table <- tidy_model %>%
-  select(term, estimate, std.error) %>%
-  tbl_summary(
-    by = NULL,
-    statistic = list(estimate ~ "{mean} ({sd})"),
-    digits = list(all_continuous() ~ 2)
-  )
-
-# Print summary table
-summary_table
-
-
 #### Save model ####
 saveRDS(
   esg_model,

### 2024-04-19 paper/paper.qmd
List of ESG Variables
Added a list of all the variables used to calculate the ESG score

@@
 
-## Source and Collection
+## Source, Collection, and Measurement
 
-The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper (CITE), which was published in July 2023. The data was collected for the year 2022.
+The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper (CITE), which was published in July 2023.
+The data was collected for the year 2022.
+This dataset was created by the authors to capture the complex landscape of ESG commitments within private equity firms.
+Additionally, data was collected from LinkedIn to replace the staff data collected in the original dataset.
+This is further detailed below.
+The dataset combines both primary and secondary sources to gather firm-specific variables.
+The final dataset's sources include Preqin and LinkedIn, with additional insights derived from an analysis of each firm's individual website to assess ESG commitments.
 
@@
 This approach rectifies the potential imbalance that could arise when averaging, where fewer factors in one category could have the same weight as a larger number in another, leading to a more balanced and comprehensive assessment of a firm's ESG practices.
-In total, 23 columns are added to calculate the ESG Score.
-A value of 0 indicates that the firm does not engage in any form of ESG, whilst a score of 23 indicates optimal ESG practices.
-APPENDIX is a list of every variable included in the calculation of the ESG Score.
+In total, 19 columns are added to calculate the ESG Score.
+A value of 0 indicates that the firm does not engage in any form of ESG, whilst a score of 19 indicates optimal ESG practices.
+@sec-variables is a list of every variable that was used in the calculation of the ESG Score.
 
@@
 The DEI column effectively captures the combined presence of these components, making the individual columns unnecessary.
-
 Next, the ESG score was calculated using the methodology detailed above.
 After doing so, all the columns used in its calculation were also deleted since they were not needed anymore.
-A snippet of the first 10 firms is seen in @tbl-1.
-Moreover, @fig-2, @fig-4, @fig-3 demonstrate the correlations between each firm characteristics, and their ESG Score.
+
+For our regression, the following variables are included:
+
+- `Total Number of Funds`: The total number of funds within the private equity firm.
+- `Fund Size`: The accumulated capital commitments across all of the private equity firm's individual funds, measured in millions of USD.
+- `IRR`: The overall Internal Rate of Return (IRR) of the private equity firm, which is a percent ranging from 0 to 100. 
+- `Staff`: The number of employees working for the private equity firm. 
+- `Average Fund Size`: The average size the funds within the private equity firm, measured in millions of USD.
+
+A snippet of the first 10 firms is seen in @tbl-1. Moreover, @fig-2, @fig-4, @fig-3 demonstrate the correlations between each firm characteristic, and their ESG Score.
 
@@
 #| message: false
-#| fig-cap: "ESG Score by IRR and Staff Count"
+#| fig-cap: "ESG Score by Staff Count and IRR"
 #| fig-pos: H
@@
 #| message: false
-#| fig-cap: "ESG Score by IRR and Staff Count"
+#| fig-cap: "ESG Score by Number of Funds and Fund Size"
 #| fig-pos: H
@@
 
-# Appendix {-}
+# Appendix
+
+## Variables used to calculate ESG {#sec-variables}
+
+Each variable below is a binary variable, meaning a 1 indicates that firm possess it, and a 0 means it does that. Each variable was added to determine a firm's ESG Score:
+
+- `HasESGonWebsite`: A dummy variable indicating whether the private equity firm has a ESG section on its website.
+- `E_Portfoliocasestudies`: A dummy variable indicating whether the private equity firm has portfolio case studies related to environmental factors.
+- `E_Media`: A dummy variable indicating whether the private equity firm’s website has media related to environmental factors.
+- `E_HasDocumentsorPages`: A dummy variable indicating whether the private equity firm has various website documents or pages related to environmental factors.
+- `S_Portfoliocasestudies`: A dummy variable indicating whether the private equity firm has portfolio case studies specifically related to social factors. 
+- `S_Media`: A dummy variable indicating whether the private equity firm has media content related to social factors.
+- `S_HasDocumentsorPages`: A dummy variable indicating whether the private equity firm has documents or dedicated pages on its website
+related to social factors.
+- `S_HasDEI`: A dummy variable indicating whether the private equity firm has a Diversity, Equity, and Inclusion (DEI) policy or
+initiatives in place. 
+- `S_10PctWomenBoardExec`: A dummy variable indicating whether the private equity firm has at least 10% women representation in its board of
+directors or executive positions. 
+- `G_Portfoliocasestudies`: A dummy variable indicating whether the private equity firm has portfolio case studies specifically related to
+governance factors.
+- `G_HasDocumentsorPages`: A dummy variable indicating whether the private equity firm has documents or dedicated pages on its website
+related to governance factors. 
+- `Other_ESGfund`: A dummy variable indicating whether the private equity firm has a dedicated fund specifically focused on ESG
+investments.
+- `Other_ESGdocument`: A dummy variable indicating whether the private equity firm has documents on its website related to ESG components that do not fit in the other 3 categories.
+- `Other_Portfoliocasestudies`: A dummy variable indicating whether the private equity firm has portfolio case studies that are related to ESG, but do not fall into the other 3 categories. 
+- `Other_ESGMedia`: A dummy variable indicating whether the private equity firm has media content related to ESG, but does not fall into the other 3 categories. 
+- `Other_ESGpolicy`: A dummy variable indicating whether the private equity firm has an official ESG policy outlining its commitment
+and approach to ESG factors. 
+- `Other_ESGreport`: A dummy variable indicating whether the private equity firm publishes regular reports specifically addressing its
+ESG performance and initiatives.
+- `Other_ESGAwards`: A dummy variable indicating whether the private equity firm has received any awards or recognition for its ESG
+practices. 
+- `Other_HasESGHeadorCommittee`: A dummy variable indicating whether the private equity firm has an appointed individual or committee responsible for overseeing ESG matters within the organisation.
 

### 2024-04-19 scripts/01-download_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Downloads the required raw data to use in data cleaning
+# Purpose: Downloads the required raw data and saves as a csv
 # Author: Krishiv Jain
 # Date: 31 March 2024
 # Contact: krishiv.jain@mail.utoronto.ca

### 2024-04-19 scripts/02-data_cleaning.R

@@ -4,7 +4,7 @@
 # Date: 31 March 2024
 # Contact: krishiv.jain@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: None
+# Pre-requisites: CSV data file from the raw_data folder
 
 #### Workspace setup ####
 library(tidyverse)
@@ -135,15 +135,16 @@ raw_data$Average_Fund_Size <- (raw_data$FundSize_Preqin/raw_data$Totalnumberoffu
 #### Calculate and Add Column for ESG Score ####
 
 raw_data$ESG_Score <- (raw_data$HasESGonWebsite + raw_data$E_Portfoliocasestudies +
-                         raw_data$E_Media + raw_data$S_Portfoliocasestudies +
-                         raw_data$S_Media + raw_data$G_Portfoliocasestudies +
+                         raw_data$E_Media + raw_data$E_HasDocumentsorPages +
+                         raw_data$S_Portfoliocasestudies + raw_data$S_Media + 
+                         raw_data$S_HasDocumentsorPages + raw_data$S_HasDEI + 
+                         raw_data$S_10PctWomenBoardExec + 
+                         raw_data$G_Portfoliocasestudies + raw_data$G_HasDocumentsorPages +
                          raw_data$Other_ESGfund + raw_data$Other_ESGdocument +
                          raw_data$Other_Portfoliocasestudies + raw_data$Other_ESGMedia +
                          raw_data$Other_ESGpolicy + raw_data$Other_ESGreport +
-                         raw_data$Other_ESGAwards + raw_data$E_HasDocumentsorPages +
-                         raw_data$S_HasDEI + raw_data$S_10PctWomenBoardExec +
-                         raw_data$S_HasDocumentsorPages + raw_data$G_HasDocumentsorPages +
-                         raw_data$Other_HasESGHeadorCommittee)
+                         raw_data$Other_ESGAwards + raw_data$Other_HasESGHeadorCommittee)
+
 
 #### Remove Columns used in Calculation ####
 raw_data$HasESGonWebsite <- NULL

### 2024-04-19 scripts/03-test_data.R

@@ -4,7 +4,7 @@
 # Date: 18 April 2024
 # Contact: krishiv.jain@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Downloaded the cleaned data file from the cleaned_data folder to run these tests
+# Pre-requisites: Downloaded the cleaned data file from the analysis_data folder to run these tests
 
 
 #### Workspace setup ####

### 2024-04-19 scripts/04-model.R

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Creates a GLM for the cleaned dataset
+# Author: Krishiv Jain
+# Date: 18 April 2024
+# Contact: krishiv.jain@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: The clean dataset from the analysis_data folder
 
 
 # Load required libraries

### 2024-04-19 other/datasheet/datasheet_template.qmd
Added Datasheet

---
title: "Datasheet for 'ESG in the Top 100 US Private Equity Firms Dataset'"
author: 
  - Krishiv Jain
thanks: "Code and data are available at: https://github.com/Krishiv-J/ESG-in-Private-Equity"
date: today
date-format: "D MMMM YYYY"
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @Gebru

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyse ESG practices of the top United States Private Equity firms. The goal was to conduct a content analysis of websites to source data on their ESG practices and assess the level of commitment and transparency among these firms.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Markarian, Garen and Rakotobe, Calvin and Semionov, Alexander, from the University of Lausanne.

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The funding source or associated grant for the creation of the dataset is not mentioned.

4. *Any other comments?*
    - The dataset was hand-collected from the websites of top U.S. private equity firms and supplemented with data from the Preqin and Bloomberg database. The focus was on a subset of 100 firms to make the data collection manageable whilst still representing a significant portion of the industry.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances represent individual private equity firms, specifically their ESG practices and related information available on their websites and from databases. Moreover, it contains firm specific characteristics, such as their size, the year they were established, their location, and more.
2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 100 instances, representing the top 100 U.S. private equity firms for the year 2022.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- The dataset is for the top 100 U.S. private equity firms out of this larger set. The top firms from taken based on a ranking from Private Equity International, a renowned organisation that publishes an annual global ranking of PE firms.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- It contains a total of 117 variables. These are firm specific characteristics used to determine a variety of different components in the paper (ESg-Score, Weighted ESG-Score, and Greenwashing)
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- Yes, IRR data was not available for all firms from Preqin. Bloomberg was used whenever data was not available on Preqin. 
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- There are certain columns that have been repeated, the reason for which is unknown. 
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- Self-contained
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The variables that were collected from Preqin would require a membership. The rest is publicly available. 
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was acquired through a content analysis of private equity firm websites and complemented with data from the Preqin and Bloomberg database.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Manual entry
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The dataset is not a sample
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Not mentioned
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Not mentioned
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- Third Parties
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- No
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- No
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Consent was not obtained.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes cleaning of the data was done.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- Yes, available at: https://github.com/Krishiv-J/ESG-in-Private-Equity/blob/main/data/raw_data/2396_ESG_Data_v1.0.dta
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- R was used.
4. *Any other comments?*
	- No

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- Yes, it was used in the authors' paper. 
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No
3. *What (other) tasks could the dataset be used for?*
	- A variety of studies regarding the top private equity firms in the United States. 
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No
6. *Any other comments?*
	- No

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- Not mentioned
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- Not mentioned
3. *When will the dataset be distributed?*
	- Not mentioned
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- Not mentioned
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- Not mentioned
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- Not mentioned
7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Not mentioned
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Not mentioned
3. *Is there an erratum? If so, please provide a link or other access point.*
	- Not mentioned
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- Not mentioned
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Not mentioned
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Not mentioned
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Not mentioned
8. *Any other comments?*
	- No

\newpage

# References

### 2024-04-19 paper/paper.qmd
Added Datasheet

@@
 ---
-title: "Top Private Equity Firms with Larger Average Fund Sizes and Lower Internal Rate of Returns (IRRs) in the United States Give ESG a Higher Importance"
-subtitle: "A reproduction using data from the United States and a case study from Europe" 
+title: "An Analysis of Top Private Equity Firms in the United States' Characteristics That Determine ESG Practices."
 author: 
@@
 date-format: long
-abstract: "Concerns have been raised that private equity firms in the United States, who make significant contributions towards both the economy and society, do not give enough importance towards ESG.
-This paper aims to improve upon the work done and data collected in the ESG in the Top 100 US Private Equity Firms paper by fixing certain data inaccuracies, and considering different variables of interest.
-The analysis is extended to a case study in Europe.
-We find that in both regions, the average fund size and their IRR can be used to make reasonable predictions about their focus on ESG, whereas the number of employees that have is irrelevant."
+abstract: "This paper aims to improve upon the work done and data collected in the ESG in the Top 100 US Private Equity Firms paper, where they analysed different determinants of private equity firm's ESG practices.
+This is done by fixing certain data inaccuracies, using a different methology to calculate a firm's ESG scores, and considering different variables of interest.
+The findings reveal that internal rate of return (IRR) and the total number of funds have an impact on ESG score, whereas the number of employees, the fund's size, and the average size of each fund have negligible impact.
+This research contributes to the understanding the ESG practices of the top private equity firms in the United States."
+
 format: pdf
@@
 
-## Weaknesses
+## Limitations
+
+There are several limitations and weaknesses.
+The original dataset, crafted by the authors of the base paper, introduces potential biases due to the subjectivity involved in data collection, such as the use on website content analysis to determine a large number of the variables.
+Even with this paper's efforts to mitigate subjectivity in this study, there are elements that retain a subjective component, particularly those collected by the original authors.
+This could influence the accuracy and reliability of the dataset used in our analysis.
+The study focuses exclusively on the top 100 U.S.-based private equity firms, which may not be representative of smaller or non-U.S.
+firms.
+This limited scope may introduce bias, potentially overlooking trends and practices in smaller or regional private equity firms that could differ from those in larger, more global firms.
+Additionally, the exclusion of certain types of firms, such as investment banks, might limit the external validity of the findings.
+For instance, discerning genuine ESG commitment from mere lip service can be challenging, potentially affecting the reliability of the ESG scores assigned to each firm.
+Moreover, the decision to opt for a summing method instead of averaging the ESG scores across categories may have implications on the interpretation of the ESG-Score.
+This methodological choice might not capture the nuances firms might have in their ESG practices.
+Furthermore, the exclusion of the Weighted ESG-Score, which was part of the original methodology, might overlook the importance of environmental factors, given the global emphasis on environmental sustainability.
+The regression results present associations rather than causality.
+Whilst the study identifies relationships between firm characteristics and ESG scores, it does not establish causative links.
+Also, using LinkedIn for gathering staff count introduces potential inaccuracies.
+Firstly, the data from LinkedIn was from 2024, whereas the rest of the metrics is from 2022.
+Moreover, the data from LinkedIn might not be up-to-date or fully reflective of the actual number of employees, given that not all employees maintain or update their LinkedIn profiles regularly.
+This could lead to an underestimation or overestimation of staff counts, affecting the analysis.
 
 ## Future Research
+
+Whilst this study has examined several firm-specific variables like fund size, IRR, and staff count, there remain other potentially influential factors that could shape ESG practices.
+For instance, firm age, geographical location, and the presence of specific ESG committees or policies might provide additional insights into the determinants of ESG scores.
+Investigating these additional variables could offer a more comprehensive understanding of the factors driving ESG commitments in private equity firms and help identify new avenues for promoting and enhancing ESG practices.
+Moreover, expanding the analysis to include firms from different regions or countries could provide valuable insights into the global trends, practices, and challenges in ESG commitments.
+Furthermore, whilst quantitative analysis provides valuable insights into the trends, patterns, and relationships between variables, incorporating qualitative methods like interviews, case studies, or stakeholder engagement could offer a richer, more nuanced understanding of the motivations, challenges, strategies, and perceptions behind ESG practices.
+Understanding the perspectives and preferences of various stakeholders, including investors, employees, communities, and industry peers, could shed light on the human aspects, motivations, and dynamics influencing ESG commitments within private equity firms.
 
@@
 
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-```{r}
-
-```
-
-## Diagnostics
-
-```{r}
-
-```
-
 \newpage

### 2024-04-19 paper/paper.qmd
Changes

@@
 ---
-title: "An Analysis of Top Private Equity Firms in the United States' Characteristics That Determine ESG Practices."
+title: "An Analysis of The Characteristics of the Top Private Equity Firms in the United States That Determine ESG Practices."
 author: 
@@
 
-library(palmerpenguins)
 library(here) 
@@
 library(gtsummary)
-
 library(boot)
@@
 
-The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper (CITE), which was published in July 2023.
+All data analysis was done through R [@citeR] with the help of the following packages: `tidyverse` [@citetidyverse], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `rstanarm` [@rstanarm], `dplyr` [@citedplyr], `gridExtra` [@gridExtra], and `janitor` [@citejanitor].
+
+The raw data set used for this paper is obtained from the “ESG in the Top 100 US Private Equity Firms” paper [@paper], which was published in July 2023.
 The data was collected for the year 2022.

### 2024-04-19 paper/paper.qmd
Final Edits

@@
 The corporate landscape is rapidly evolving, with a notable shift towards greater responsibility and transparency, spurred by the rise of Environmental, Social, and Governance (ESG) considerations.
-While ESG has gained traction in publicly traded companies, there is a significant gap in understanding the ESG practices of private equity (PE) firms, despite their immense global impact.
+Whilst ESG has gained traction in publicly traded companies, there is a significant gap in understanding the ESG practices of private equity (PE) firms, despite their immense global impact.
 This gap is particularly surprising given the influential role PE firms play in the economy and their potential impact on ESG.
@@
 
-This paper aims to reproduce the Top 100 US Private Equity Firms paper.
+This paper aims to reproduce the ESG in Top 100 US Private Equity Firms paper, and uses the dataset that were constructed by its authors [@paper].
 That paper focuses on the top 100 PE firms based in the United States, conducting a thorough analysis of their ESG practices through content analysis of their websites.
-The findings reveal a notable lack of comprehensive ESG disclosures among PE firms, with only a minority providing substantial information on their environmental, social, and governance initiatives.
-This paper aims to improve upon their work by firstly amending the data collected for certain variables, such as number of employees.
-Next, this paper calculates next metrics, such as average fund size.
-Lastly, the paper focuses on different predictor variable.
-The reasons for each improvement is detailed in the paper.
+This paper aims to build upon their work by firstly amending the data collected for certain variables, such as number of employees.
+Secondly, this paper calculates new metrics, such as average fund size.
+Thirdly, a new methodology is used to calculate a firm's ESG score.
+Lastly, the paper focuses on different predictor variables.
+The reasons for each modification is detailed in the paper.
 
@@
 This paper is structured as follows.
-In Section 2, the source of the data, the methodology of data collection and cleaning, and the changes made to the data set is detailed.
-Section 3 discusses the choice and construction of our logistic model to make predictions about private equity firms.
-Section 4 presents the model's results.
-Section 5 draws upon the relevance of these results to Europe.
-Section 6 talks about the implications, ethical considerations, and limitations of our work.
+In @sec-data, the source of the data, the methodology of data collection and cleaning, and the changes made to the data set is detailed.
+@sec-model discusses the choice and construction of our negative model.
+@sec-results presents the model's results.
+@sec-discussion further discusses the results, comparing it to the original paper, and discusses the limitations of the paper
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-# Results
+# Results {#sec-results}
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
